Complex Quasiperiodic Variables from Four Years of TESS

### 2023-06-13 paper/ms.tex
update ms

\received{---}
\revised{---}
\accepted{---}
\shorttitle{Cycle 1-4 CQVs}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence M-dwarfs
  with almost-periodic optical modulation that includes both sharp and broad
  troughs.  The troughs are usually superposed on smooth, spot-like
  modulation.  Based on a lack of observed infrared excesses, these
  objects do not have primordial gas-rich disks.  Nonetheless, the
  currently preferred explanations for their optical variability invoke
  long-lived material that orbits at the corotation radii, for
  instance transiting dust clumps or stellar prominences.  Here, we
  report new CQVs discovered in the 120-second cadence TESS data
  collected between July~2018 and Sep~2022 (Sectors 1-55).  Our search
  used two methods, the first based on counting dips in phase-folded
  light curves, and the second based on counting peaks in the Fourier
  domain.  From our analysis of \nstarssearched\ M-dwarfs with
  $T$$<$16 and $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CQVs.
  Most of these discoveries are new, and they include the brightest
  ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
  class of variable star known.  A few objects are ``outliers among
  outliers''; for instance LP 12-502 shows between four and eight
  local minima per cycle, distributed over a ``dip complex'' with
  fixed total duration over more than one thousand cycles, but that
  has a detailed shape that at times showed significant changes over only one
  cycle.  More generally, we find that exactly zero of the CQVs
  maintain an identical light curve morphology over timescales of more
  than a few hundred cycles.  While the physical explanation behind
  these objects remains enigmatic, our sample is a step toward the
  spectroscopic and demographic studies that may help clarify their
  origin.  Connections to star, disk, and
  exoplanet evolution are emphasized.
\end{abstract}

@@

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show quasiperiodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation.  Some of the objects show up to eight local
minima (dips) per cycle; sharp peaks are also common.  Most of these
variable stars turn out to be pre-main-sequence M-dwarfs without
near-infrared excesses, with ages of $\approx$5-150 million years
(Myr), and rotation periods of at most two days; they are observed to
be $\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2023ApJ...945..114P}.

@@

A point on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S,2018AJ....155...63S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs are not ``dippers'', which are classical T Tauri stars with
infrared excesses whose optical variability is linked to obscuring
inner disk structures and accretion hot spots (CITE Cody2014,
ConnorRobinson2021).  At the risk of introducing yet another standard,\footnote{\url{https://xkcd.com/927/}}
we prefer to make the
technical distinction that the CQVs are, over timescales of more than
a few cycles, not exactly periodic.  Their shapes evolve, usually over
some decoherence timescale, similar to variability induced by surface
inhomogeneities such as starspots.  While the three-type
classification scheme proposed by \citet{2017AJ....153..152S} may
indeed provide some helpful visual distinctions among the CQV class,
it seems likely (we hope!) that they are all explained by a single
underlying phenomenon, and so we opt to refer to them by a single
empirically descriptive name.

@@

To assess the completeness of the resulting 120-second cadence data that we
analyze, we cross-matched TIC8 \citep{2018AJ....156..102S} against the
Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.   We opted
for Gaia DR2 rather than DR3 because the base catalog for TIC8 was
Gaia DR2, which facilitated a one-to-one crossmatch using the Gaia source
identifiers.  This exercise showed that for $T$$<$16 M-dwarfs, the TESS
2-minute data are roughly 50\% complete at $\approx$50\,pc.  At
$<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs have at least one
sector of short-cadence data; at $>$100\,pc, $\lesssim$10\% of such
M-dwarfs have at least one sector of short-cadence data.  Armed
with this understanding, we then used
our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16\\
  G_{\rm BP} - G_{\rm RP} &> 1.5 \\
  M_{\rm G} &> 4 \\
  d &< 150\,{\rm pc},
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the parallax
and ignoring any small zero-point corrections.
This selection function includes dwarf stars later than spectral types
of $\approx$K6V.  Hereafter, we will refer to this set of stars as the
target sample, and it includes \nstarssearched\ stars with (roughly)
M-dwarf spectral type, down to $T$$<$16 and out to $d$$<$150\,pc.

@@

		\vspace{-0.15cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
	\end{center}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.
		The ``clump'' or ``prominence'' scenarios seem most plausible,
		given the stability of the phenomenon and the lack of observed infrared excesses.
	}
	\label{fig:f1}
\end{figure*}

@@

Previous methods that have yielded CQV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach is followed by
visual vetting, since most rapid rotators with many Fourier harmonics
are false positives such as eclipsing binaries or multiple stars
blended into a single photometric aperture.  In this work, we adopted
the Fourier approach, and also implemented a new search approach based
on counting the number of sharp local minima in phase-folded light
curves.  We then applied these two search techniques independently.

@@

We then identified local minima in the resulting residual light curve
using the SciPy \texttt{find\_peaks} utility (CITE), which is based on
comparing adjacent values in an array.  For a peak to be flagged as
significant, we required it to have a width of at least $0.02\,P$, and
a height of at least twice the point-to-point RMS.  This latter
quantity is defined as the 68$^{\rm th}$ percentile of the
distribution of the residuals from the median value of $\delta f_i
\equiv f_i - f_{i+1}$, where $f$ is the flux and $i$ is an index over
time.

@@

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and blended combinations thereof.
Rarer false positives included disk-induced variability, for instance
induced by quasiperiodic dippers (CITE).  Typical false postive rates
from our dip-counting pipeline were 5:1, with 368 unique stars
flagged, and about 20\% being labelled either ``good'' or ``possible''
CQVs; for the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ
unique stars flagged, and NN\% being labelled ``good'' or ``possible''
CQVs}.

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0019_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CQVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence.
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima; 
      one of the four sharp dips for this star was not identified!
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}

>>>>

\received{---}
\revised{---}
\accepted{---}
\shorttitle{Four Years of CQVs}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence
  M-dwarfs with almost-periodic optical modulation that includes both
  sharp and broad troughs.  The troughs are usually superposed over
  smooth, spot-like modulation.  Based on a lack of observed infrared
  excesses, these objects do not have primordial gas-rich disks.
  Nonetheless, the currently preferred explanations for their optical
  variability invoke long-lived material in orbit at the corotation
  radius, for instance transiting dust clumps or stellar prominences.
  Here, we report new CQVs discovered in TESS data collected between
  July~2018 and Sep~2022.  Our search used two methods, the first
  based on counting dips in phase-folded light curves, and the second
  based on counting peaks in the Fourier domain.  From our analysis of
  \nstarssearched\ M-dwarfs with $T$$<$16 and $d$$<$150\,pc, we find
  \ncpvsfound\ gold-standard CQVs.  Most of these discoveries are new,
  and they include the brightest ($T$$\approx$10) and closest
  ($d$$\approx$20\,pc) examples of this class of object known.  A few
  objects are ``outliers among outliers''; for instance LP 12-502
  shows four to eight local minima per cycle, distributed over a ``dip
  complex'' with a total duration that is fixed over more than one
  thousand cycles, but with a detailed shape that exhibited changes
  over less than one cycle.  More generally, we find that none of the
  CQVs maintain a fixed light curve shape over timescales of more than
  a few hundred cycles -- hence, {\it quasi}periodic.  Although the
  physical explanation behind these objects remains enigmatic, our
  sample may help clarify their origin.  Connections to star, disk,
  and exoplanet evolution are emphasized.
\end{abstract}

@@

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show quasiperiodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation.  Some of the objects show up to eight local
minima (dips) per cycle; sharp peaks are also common.  Most of these
variable stars turn out to be pre-main-sequence M-dwarfs without
near-infrared excesses, with ages of $\approx$5-150 million years
(Myr), and rotation periods of at most two days; they are observed to
be $\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.

@@

A point on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S,2018AJ....155...63S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs are not ``dippers'', which are classical T Tauri stars with
infrared excesses whose optical variability is linked to obscuring
inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
introducing yet another
standard,\footnote{\url{https://xkcd.com/927/}} we prefer to make the
technical distinction that the CQVs are, over timescales of more than
a few cycles, not exactly periodic.  Their shapes evolve, usually over
some decoherence timescale, similar to variability induced by surface
inhomogeneities such as starspots.  While the three-type
classification scheme proposed by \citet{2017AJ....153..152S} may
indeed provide some helpful visual distinctions among the CQV class,
it seems likely (we hope!) that they are all explained by a single
underlying phenomenon, and so we opt to refer to them by a single
empirically descriptive name.

@@

To assess the completeness of the resulting 120-second cadence data
that we analyze, we cross-matched TIC8 \citep{2018AJ....156..102S}
against the Gaia DR2 point-source catalog \citep{2018A&A...616A...1G}.
We opted for Gaia DR2 rather than DR3 because the base catalog for
TIC8 was Gaia DR2, which facilitated a one-to-one crossmatch using the
Gaia source identifiers.  This exercise showed that for $T$$<$16
M-dwarfs, the TESS 2-minute data are roughly 50\% complete at
$\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\% of the $T$$<$16 M-dwarfs
have at least one sector of short-cadence data; at $>$100\,pc,
$\lesssim$10\% of such M-dwarfs have at least one sector of
short-cadence data.  Armed with this understanding, we then used our
cross-match between Gaia DR2 and TIC8 to select our stars of interest,
which we defined as stars with 120-second cadence TESS light curves
that satisfied
\begin{align}
  T &< 16\\
  G_{\rm BP} - G_{\rm RP} &> 1.5 \\
  M_{\rm G} &> 4 \\
  d &< 150\,{\rm pc},
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  This selection
function includes dwarf stars later than spectral types of
$\approx$K6V.  This target sample includes \nstarssearched\ stars with
approximately M-dwarf spectral type, down to $T$$<$16 and out to
$d$$<$150\,pc.

@@

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
	\end{center}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
    {\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
    stacked over one month.  Gray are raw 2-minute data; black bins to
    300 points per cycle.  Periods in hours are in the bottom right of
    each panel.  In order left-to-right, the objects are LP 12-502
    (TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
    425933644 (Sector~28).
    {\it Bottom:} Plausible cartoon models for the phenomenon.  The
    ``clump'' or ``prominence'' scenarios seem most plausible, given
    the stability of the phenomenon and the lack of observed infrared
    excesses.
	}
	\label{fig:f1}
\end{figure*}

@@

Previous methods that have yielded CQV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach requires visual
vetting, since most rapid rotators with many Fourier harmonics are
false positives such as eclipsing binaries or multiple stars blended
into a single photometric aperture.  In this work, we implemented a
new search approach based on counting the number of sharp local minima
in phase-folded light curves, while also using the previously tested
Fourier approach.  We applied these two search techniques
independently.

@@

We then identified local minima in the resulting residual light curve
using the SciPy \texttt{find\_peaks} utility
\citep{2020NatMe..17..261V}, which is based on comparing adjacent
values in an array.  For a peak to be flagged as significant, we
required it to have a width of at least $0.02\,P$, and a height of at
least twice the point-to-point RMS.  This latter quantity is defined
as the 68$^{\rm th}$ percentile of the distribution of the residuals
from the median value of $\delta f_i \equiv f_i - f_{i+1}$, where $f$
is the flux and $i$ is an index over time.

@@

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and variability from neighboring,
off-target stars.  Typical false postive rates from our dip-counting
pipeline were 5:1, with 368 unique stars flagged, and about 20\% being
labelled either ``good'' or ``possible'' CQVs; for the Fourier
pipeline, {\bf the rate was X:Y, with ZZZZ unique stars flagged, and
NN\% being labelled ``good'' or ``possible'' CQVs}.

@@

%\clearpage

\software{
  %\texttt{arviz} \citep{arviz_2019},
  %\texttt{altaipony} \citep{ilin_flares_2021},
  \texttt{astrobase} \citep{2021zndo...1011188B},
  %\texttt{astroplan} \citep{astroplan2018},
	%\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  %\texttt{astropy} \citep{astropy_2018},
  %\texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  %\texttt{ceres} \citep{brahm_2017_ceres},
  %\texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  %\texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  %\texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  %dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  % 	exoplanet:theano},
	%\texttt{gala} \citep{gala,PriceWhelan_2017_gala_zenodo},
	%\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  %\texttt{IPython} \citep{perez_2007},
	%\texttt{isochrones} \citep{morton_2015_isochrones},
	%\texttt{lightkurve} \citep{lightkurve_2018},
  %\texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  %\texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  %\texttt{numpy} \citep{walt_numpy_2011}, 
  %\texttt{pandas} \citep{mckinney-proc-scipy-2010},
  %\texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  %\texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{2020NatMe..17..261V},
  \texttt{TESS-point}  \citep{2020ascl.soft03001B},
  %\texttt{tesscut} \citep{brasseur_astrocut_2019},
  %\texttt{unpopular} \citep{hattorio_2021_cpm},
  %\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  %\texttt{webplotdigitzer} \citep{rohatgi_2019},
  %\texttt{wotan} \citep{hippke_wotan_2019}.
}
\

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2018A&A...616A...1G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
 	%Keck:II~(NIRC2).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
	%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
  %PFS ({\bf CITE}),
	%Tillinghast:1.5m~(TRES).
  %MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
	%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
	%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
 	Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
 	%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
%	  ASTEP:0.40$\,$m (ASTEP400),
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
%	  El Sauce:0.356$\,$m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
%	  Kepler,
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
%   MuSCAT3 \citep{Narita_2020},
% 	NTT,
% 	SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
%    ZTF.
}

\bibliographystyle{yahapj}                            
\bibliography{bibliography}

@@

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0018_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CQVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      Dotted lines show up to the 10$^{\rm th}$ harmonic and
      subharmonic.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence, in
      Barycentric TESS Julian Date (BTJD).
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima.
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      {\it m)}: BANYAN-$\Sigma$ v1.1 association probabilities, calculated
      using positions, proper motions, and the parallax.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}
